Novelty Detection Using Graphical Models for Semantic Room Classification

### 2011-06-02 semantic-nd/article.tex
Added .jpgs in .pdf format
Commit changes in article that were stashed (I had forgotton about them).

\begin{figure}[h]
\centering
\includegraphics[width=0.9\textwidth]{figures/conceptual-layer.jpg}
\caption{\label{fig:conceptual-layer}Interaction of the sub-systems
         in Dora with special focus on the conceptual layer.}
\end{figure}

@@

\begin{figure}[h]
\centering
\includegraphics[width=0.90\textwidth]{figures/chain-graph.png}
\caption{\label{fig:chain-graph}Example chain-graph produced by the \emph{conceptual layer}.}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Novelty Detection}
\label{sec:novelty-detection}
% Introduce novelty detection
Novelty detection deals with detecting that a new input was generated by a class
other than the ones the system knows about~\cite{markou2003novelty}.
It is harder than classification as only positive samples of a class are available
rendering normal classification methods invalid.

>>>>

\begin{figure}[h]
\centering
\includegraphics[width=0.9\textwidth]{figures/processes.pdf}
\caption{\label{fig:conceptual-layer}Interaction of the sub-systems
         in Dora with special focus on the conceptual layer.}
\end{figure}

@@

\begin{figure}[h]
\centering
\includegraphics[width=0.80\textwidth]{figures/chaingraph.pdf}
\caption{\label{fig:chain-graph}Example chain-graph produced by the \emph{conceptual layer}.}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Novelty Detection}
\label{sec:novelty-detection}
% Introduce novelty detection
Novelty detection deals with detecting that a data sample belongs to a class
originated by a distribution other than the ones the system knows about \citep{markou2003novelty}.
It is harder than classification as only positive samples of the class are available
rendering normal classification methods unusable.
